MSF_Groupwork-NBA_shotlog

### 2016-10-11 MSFGroupwork-NBAHotHand.Rmd
minor changes

game[, "FG%"] <- NA 
for (i in 1:nrow(game)){
  game[i, "FG%"] <- round(((game[i, "1"]/game[i, "FGA"]) * 100), digits = 2)
}

#Team <- rep(NA, (lastGamesID - firstGamesID + 1) * 2)
#FG_Percentage <- rep(NA, (lastGamesID - firstGamesID + 1) * 2)
#for(i in 21400001:21400908){
#  j = i - 21400001 +1 # 
#  game <- df[, df[, "GAME_ID1"] == i]
#  home <- game[, game["LOCATION"] == "H"]
#  home.p <- count(home[, home[, "SHOT_RESULT"] == 1]) / nrow(home)
#  away <- game[, game["LOCATION"] == "A"]
#  away.p <- count(home[, home[, "SHOT_RESULT"] == 1]) / away(home)
#  FG_Percentage[j] <- home.p
#  FG_Percentage[j + 1] = away.p
#  Team[j] = "H"
#  Team[j + 1] = "A"
#}

>>>>

game[, "FG%"] <- NA 
for (i in 1:nrow(game)){
  game[i, "FG%"] <- round(((game[i, "1"]/game[i, "FGA"]) * 100), digits = 2)
}
```
